Depth comparison Seymour + Hollyburn green -> orange runnels

### 2020-01-13 code/exploratory/depth_comparison.Rmd
organize

```{r include=F}
rbcl_rel_abund <- read_csv(here("data/03_filtered/rbcl/depth_rbcl_rel_abund.csv"))
s18_all_rel_abund <- read_csv(here("data/03_filtered/18s/depth_18s_rel_abund.csv"))

@@

```{r output, include=FALSE}
ggsave(filename = here("manuscript/figs/4_depth_comparison/rbcl.pdf"), plot=depth)
```

>>>>

```{r include=F}
rbcl_rel_abund <- read_csv(here("data/"))
s18_all_rel_abund <- read_csv(here("data/03_filtered/18s/depth_18s_rel_abund.csv"))

@@

```{r output, include=FALSE}
#ggsave(filename = here("manuscript/figs/4_depth_comparison/rbcl.pdf"), plot=depth)
```

### 2020-01-13 code/exploratory/green-orange.Rmd
organize

---
title: "Depth sample comparison"
output: html_notebook
---

```{r}
library(tidyverse)
library(here)
```

```{r include=F}
rbcl_rel_abund <- read_csv(here("data/"))
s18_all_rel_abund <- read_csv(here("data/03_filtered/18s/depth_18s_rel_abund.csv"))

rbcl_tax <- read_csv(here("data/02_tidied/tidied.rbcl_taxonomy.csv"))
s18_tax <- read_csv(here("data/02_tidied/tidied_silva_18s_assignments.csv"))

rbcl_otus <- read_csv(here("output/asv_otu_key.csv"))

field <- read_csv(here("data/02_tidied/tidied_field.csv"))
```

```{r rbcl_wrangle, include=F}
rbcl <- rbcl_rel_abund %>% 
  left_join(rbcl_tax, by="asv_id") %>% 
  left_join(field, by="sample_id") %>% 
  left_join(rbcl_otus, by="asv_id")
glimpse(rbcl)
rbcl %>% distinct(sample_id, alias, depth_cm)

depth_sample_info <- rbcl %>% 
  distinct(sample_id, alias, depth_cm) %>% 
  mutate(depth_chr = if_else(is.na(depth_cm), "surface", "sub-surface"),
         top_sample = case_when(alias == "H2.10"~"H2.10*", # add a star, same site, but different date
                                alias == "H3.4"~"H2.10*",
                                alias == "H4.3"~"H4.4",
                                alias == "S9.2"~"S9.1",
                                TRUE ~ alias)) %>% 
  select(sample_id, top_sample, depth_chr)
depth_sample_info

rbcl_1 <- rbcl %>% 
  left_join(depth_sample_info, by="sample_id") %>% 
  group_by(top_sample, depth_chr, otu_name) %>% 
  summarise(rel_abund= sum(rel_abund)) %>% 
  ungroup()

rbcl_1
```

>>>>

---
title: "Depth comparison Seymour + Hollyburn green -> orange runnels"
output: html_notebook
---
```{r}
library(tidyverse)
library(here)
```

```{r include=F}
rbcl_ra_depth <- read_csv(here::here("data/rel_abund/3_filter/rbcl/depth_rbcl_rel_abund.csv")) # only the "depth samples", see code/wrangle/filter_rbcl_rel_abund.R for selection criteria
rbcl_ra_main <- read_csv(here:::here("data/rel_abund/3_filter/rbcl/rbcl_rel_abund.csv"))
s18_all_rel_abund <- read_csv(here::here("data/rel_abund/3_filter/18s/depth_18s_rel_abund.csv"))
# rbcl_tax <- read_csv(here::here("data/taxonomy/tidied.rbcl_taxonomy.csv"))
s18_tax <- read_csv(here::here("data/taxonomy/tidied_silva_18s_assignments.csv"))
rbcl_otus <- read_csv(here::here("data/otus/otu_rbcl_asvs.csv"))
field <- read_csv(here::here("data/field/tidy_field.csv"))
```

```{r rbcl_wrangle, include=F}
rbcl <- rbcl_ra_depth %>%
  bind_rows(rbcl_ra_main) %>%
  left_join(field, by="sample_id") %>%  
  left_join(rbcl_otus, by="asv_id") %>% 
  filter(alias %in% c("S9.2", "S9.1", "S6.7", "S2.2","H2.10","H3.4")) %>% # choose just six samples
  # excluded H4.3, H4.4 because dominated by Chlainomonas, I want to focus on Chloro krienitzii samples
  mutate(depth = case_when(alias == "S9.2"~"surface", # add new category, whether its surface or subsurface
                           alias == "S9.1"~"depth",
                           alias == "S6.7"~"surface",
                           alias == "S2.2"~"depth",
                           alias == "H2.10"~"surface",
                           alias == "H3.4"~"depth"))

# rbcl %>% distinct(alias, depth, depth_cm)

# select variables of interest, group by otus
rbcl_1 <- rbcl %>% 
  group_by(alias, otu_name, depth) %>% 
  summarise(rel_abund= sum(rel_abund)) %>% 
  ungroup() %>% 
  select(alias, depth, otu_name, rel_abund)

```
